In-Rank mesh optimization for URL customized promotion in SEO

### 2015-03-03 MY_PAPERS/article_sduprey_iswag_02_06_2014.tex
iswag

search engine, e-commerce, page rank, in rank, mesh optimization, global optimization, Hadoop, Spark GraphX, Neo4j

@@

The structure found is as we expected : home followed by metalists, lists and then products.

@@

>>>>

search engine optimization, e-commerce, page rank, in rank, mesh optimization, global optimization, Hadoop, Spark GraphX, Neo4j

@@

The structure found is as we expected arborescent : home linking to metalists, metalists linking to lists and lists to products.
\textbf{\large Optimal site structure}
\epsfig{file=site_structure.eps,height=5cm,width=5cm}

@@

Mesh optimization is a key concept for SEO. Numerical experiments on a small case example show the relevance and the possibility to actually improve your site mesh
to push forward pages accordingly to an importance metrics. This importance metrics is yours to define. The difficulty here does not lie in the
theorical conception of the algorithm, but rather in its distributed implementation on a big data platform. The choice of open source solutions
is here highlighted. It allows a fast ramp-up for anyone to a high level technological state without reinventing the wheel.
